Incentives are the biggest barriers to widespread data sharing

### 2021-08-11 new-paper.Rmd
add citations for data sharing in biology and psychology

Despite the increase in data being shared alongside publications, the status quo of data sharing in science is not good. [@Rowhani-Farid2016] showed that 7 of 157 (4.5%) sampled papers in the British Medical Journal shared data, and only 14% of articles claiming open sharing of data actually shared their data. Similarly, [@Stodden2018] showed only 36% of papers in the journal *Science* shared data, despite the Journal's data sharing policy. [@Colavizza2020] reflects similar findings for PLOS and BMC journals. There are numerous examples of similar problems in other fields, such as psychology, biology, and bioinformatics. The reality is that while data sharing is increasing in many fields such as ecology, the amount of data that can be reused is likely lower. To make shared data useful, we need to realign incentives for researchers.

>>>>

Despite the increase in data being shared alongside publications, the status quo of data sharing in science is not good. [@Rowhani-Farid2016] showed that 7 of 157 (4.5%) sampled papers in the British Medical Journal shared data, and only 14% of articles claiming open sharing of data actually shared their data. Similarly, [@Stodden2018] showed only 36% of papers in the journal *Science* shared data, despite the Journal's data sharing policy. [@Colavizza2020] reflects similar findings for PLOS and BMC journals. There are numerous examples of similar problems in other fields, such as psychology [@vanpaemel2015] and biology [@schofield2009]. The reality is that while data sharing is increasing in many fields such as ecology and genomics, the amount of data that can be reused is likely lower. To make shared data useful, we need to realign incentives for researchers.
